### 2021-09-27 paper/main.tex
Add manuscript source

\documentclass[twoside]{article}

%\usepackage{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
\usepackage{aistats2022}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

% If you set papersize explicitly, activate the following three lines:
%\special{papersize = 8.5in, 11in}
%\setlength{\pdfpageheight}{11in}
%\setlength{\pdfpagewidth}{8.5in}

% If you use natbib package, activate the following three lines:
\usepackage[round]{natbib}
\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

% If you use BibTeX in apalike style, activate the following line:
%\bibliographystyle{apalike}

\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}

\usepackage{acronym}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbold}
\usepackage{booktabs}
\usepackage{color}
\usepackage{fontawesome}
\usepackage{graphics}
\usepackage{microtype}
\usepackage{nicefrac}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{dsfont}
\usepackage{tcolorbox}

\newtcolorbox{custombox}[1][]
{
  colframe=blue!40,
  colback=blue!8,
  left=2pt,
  right=2pt,
  top=2pt,
  bottom=2pt,
  \centering #1
}

\newcommand{\gilles}[1]{\textcolor{orange}{GL: #1}}
\newcommand{\antoine}[1]{\textcolor{green}{AW: #1}}
\newcommand{\joeri}[1]{\textcolor{red}{JH: #1}}
\newcommand{\arnaud}[1]{\textcolor{blue}{AD: #1}}
\newcommand{\old}[1]{\textcolor{magenta}}

% Custom definitions
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\logit}{\sigma^{-1}}
\DeclareMathOperator{\sigmoid}{\sigma}
\DeclareMathOperator{\vtheta}{\boldsymbol\vartheta}
\DeclareMathOperator{\vx}{\boldsymbol x}
\renewcommand*{\d}[1]{\operatorname{d}\!{#1}}

\newcommand{\code}[1]{\href{#1}{\includegraphics[scale=0.8,trim=0 0.05cm 0 0]{figures/code}}}

\newcommand{\nre}{\textsc{nre}}
\newcommand{\snre}{\textsc{snre}}
\newcommand{\npe}{\textsc{npe}}
\newcommand{\snpe}{\textsc{snpe}}
\newcommand{\kl}{\textsc{kl}}
\newcommand{\nf}{\textsc{nf}}

\begin{document}

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
\runningtitle{Towards Drawing Scientific Conclusions with Simulation-Based Inference }

% If your paper is accepted and the number of authors is large, the
% style will print as headings an error message. Use the following
% command to supply a shorter version of the authors names so that
% they can be used as headings (for example, use only the surnames)
%
%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}

\twocolumn[

\aistatstitle{Averting A Crisis In Simulation-Based Inference}

\aistatsauthor{%
  Joeri Hermans*\\
  %Montefiore Institute\\
  University of Li{\`e}ge\\
  \texttt{joeri.hermans@doct.uliege.be} \\
  % examples of more authors
  \And
  Arnaud Delaunoy*\\
  %Montefiore Institute\\
  University of Li{\`e}ge\\
  \texttt{a.delaunoy@uliege.be} \\
  \AND
  François Rozet \\
  University of Li{\`e}ge\\
  \texttt{francois.rozet@uliege.be} \\
  \And
  Antoine Wehenkel \\
  %Montefiore Institute\\
  University of Li{\`e}ge\\
  \texttt{a.wehenkel@uliege.be} \\
  \And
  Gilles Louppe \\
  %Montefiore Institute\\
  University of Li{\`e}ge\\
  \texttt{g.louppe@uliege.be} \\
}

\aistatsaddress{%
}]

\begin{abstract}

%   In recent years a myriad of simulation-based inference algorithms have been developed
%   with the objective to produce approximations as close as possible to the ground truth.
%   In this work we take the position that minimizing a divergence between the approximation and an unknown ground truth can incorrectly drive scientific inquiry. Instead, we argue for conservativeness. Approximations should therefore always convey at least as much uncertainty as the ground truth, and never be overconfident. We assess conservativeness by measuring coverage and showcase through extensive experiments that various approaches in simulation-based inference can produce non-conservative posterior estimators. We show empirically that ensembles consistently help in this regard but can still lead to non-conservative posterior estimators. Finally, we discuss several perspectives and open avenues of research towards conservative estimators.

% My pass:
%
%
%Computer simulators are at the center of many scientific disciplines.
%Although modern simulators are able to describe complex processes, they are less suited
%for statistical inference. 
%At the core of this problem lies the intractable likelihood model implicitly defined by the simulator's computer code. 
%To deal with this intractability,
%a myriad of Bayesian inference algorithms have been developed to approximate
%posteriors as possible to their unknown ground truths. The only requirement of these algorithms being that generating simulations is possible.
%In this work, we take the position that minimizing a divergence between the approximation and an unknown ground truth can incorrectly drive scientific inquiry. Instead, we
%argue for conservative approximations, meaning that they should always convey at least as much uncertainty as the ground truth. We collect extensive
%empirical evidence spanning months of computation on several computer clusters. Our results indicate that all benchmarked techniques produce non-conservative posterior
%approximations. Complicating their applicability.
%We show that ensembles are consistently more reliable in this regard, but can still lead to non-conservative
%estimators. Our study is complemented with new research proposals to strengthen the
%application of simulation-based inference in the sciences.

%\joeri{Reworked Gilles' proposal a bit. See below.}

% 
% Joeri's proposal after Gilles' proposal
%
%

%Recent years have seen tremendous innovations in the field of Bayesian simulation-based inference.
%{\color{blue} This work takes a step back by assessing the reliability of these algorithms to scientific use-cases concerned with constraining parameters, as is often the case in the physical sciences.??? We present...}
%This work presents extensive empirical evidence that all benchmarked algorithms -- including \textsc{(s)nre}, \textsc{(s)npe}, \textsc{snl} and various forms of \textsc{abc} -- produce non-conservative posterior approximations. Making these algorithms demonstrably unreliable if one's scientific goal is to constrain parameters of interest, as is often the case in the physical sciences. Our results further demonstrate that ensembles are consistently more reliable in this regard, although they may still lead to non-conservative posterior approximations.
%We argue that failing to address this issue will lead to a well-founded distrust in simulation-based inference. For this reason we argue that research efforts should now focus on theoretical and methodological advances to guarantee conservative approximate inference.

%
% Gilles proposal
%
We present extensive empirical evidence showing that current Bayesian simulation-based inference algorithms are inadequate for the falsificationist methodology of scientific inquiry.
Our results collected through massive experimental computations show that all benchmarked algorithms -- \textsc{(s)npe}, \textsc{(s)nre}, \textsc{snl} and variants of \textsc{abc} -- may produce overconfident posterior approximations, which makes them demonstrably unreliable and dangerous if one's scientific goal is to constrain parameters of interest. %, as is often the case in the physical sciences.
We believe that failing to address this issue will lead to a well-founded trust crisis in simulation-based inference.
For this reason, we argue that research efforts should now focus on theoretical and methodological developments of conservative approximate inference algorithms and present research directions towards this objective.
In this regard, we show empirical evidence that ensembles are consistently more reliable.

% \\\joeri{Which version? Merge?}

% In recent years a myriad of simulation-based inference algorithms have been developed to perform Bayesian inference with an intractable likelihood implicitly defined by a simulator. Those algorithms traditionally have as objective to produce approximate posterior over the quantity to be inferred as close as possible to the ground truth posterior. In this work, we take the position that minimizing a divergence between the approximation and an unknown ground truth can lead to overconfident approximations and hence incorrectly drive scientific inquiry. Instead, we argue for conservativeness meaning that approximations should therefore always convey at least as much uncertainty as the ground truth, and never be overconfident. Our main contribution lies in the generation through month of computation of extensive empirical evidence that all currently existing approaches in simulation-based inference can produce non-conservative posterior estimators and are hence not suited for scientific purpose as they are. We show empirically that ensembles consistently help in this regard but can still lead to non-conservative posterior estimators and discuss several perspectives and open avenues of research towards conservative estimators.

\end{abstract}

\section{Introduction}

% Many scientific disciplines rely on computer simulations to study complex phenomena under various conditions. 
% Although modern simulators can generate realistic synthetic observables through detailed descriptions of their data generating processes, 
% they are unfortunately not suitable for statistical inference.
% At the core of this issue lies the likelihood model $p(\vx\vert\vtheta)$ implicitly defined by 
% computer code describing the data generating processes.
% The direct evaluation of the likelihood rests on the \emph{intractable} integration of all stochastic execution paths, rendering statistical inference based on the likelihood impractical.
% Fortunately, inference remains possible by relying on likelihood-free \emph{approximations} \citep{cranmer2020frontier}
% within a field referred to as simulation-based or likelihood-free inference.

Many scientific disciplines rely on computer simulations to study complex phenomena under various conditions. 
Although modern simulators can generate realistic synthetic observables through detailed descriptions of their data generating processes, they are unfortunately not suitable for statistical inference.
The computer code describing the data generating processes defines the likelihood function $p(\vx\vert\vtheta)$ only implicitly, and its direct evaluation requires the often \emph{intractable} integration of all stochastic execution paths.
In this problem setting, statistical inference based on the likelihood function becomes impractical, but approximate inference remains possible by relying on likelihood-free \emph{approximations}, as pushed forward by the rapidly expanding field of simulation-based inference \citep{cranmer2020frontier}.

While simulation-based inference targets domain sciences, advances in the field are mainly driven from a machine learning perspective.
The field, therefore, inherits the quality assessments \citep{lueckmann2021benchmarking} customary to the machine learning literature, such as the minimization of classical divergence criteria. 
Despite recent developments of post hoc diagnostics to inspect the quality of likelihood-free approximations \citep{cranmer2015approximating, Brehmer:2018eca, brehmer2019mining, Hermans:2020skz, lueckmann2021benchmarking, sbc, dalmasso2020confidence}, assessing whether approximate inference results are sufficiently reliable for scientific inquiry remains largely unanswered whenever fitting criteria are not globally optimized or whenever the data is limited.
In fact, domain sciences, and more specifically the physical sciences, are not necessarily interested in \emph{accuracy} or \emph{correctness} of an approximation. 
Instead, in the tradition of Popperian falsification, they often seek to {\bfseries constrain parameters} of interest as much as possible at a given confidence level. 
Scientific examples include frequentist confidence intervals on the mass of the Higgs boson \citep{aad2012observation}, Bayesian credible regions on cosmological parameters \citep{gilman2018probing,Planck:2018vyg}, or constraints on the intrinsic parameters of binary black hole coalescences \citep{abbott2016gw151226}.
From a Bayesian perspective, this implies that statistical approximations in simulation-based inference should ideally come with \emph{conservative} guarantees to not produce credible regions smaller than they should be, even if it incurs a loss in statistical power.
Wrongly constraining model parameters would otherwise impede scientific inquiry.

In this work, we measure the quality of the credible regions computed through various Bayesian techniques in simulation-based inference and do so through the notion of \emph{coverage}. 
We frame our main contribution as the collection of extensive empirical evidence that required months of computation. 
Our results demonstrate that all benchmarked techniques can produce non-conservative credible regions, highlighting the need for a new class of conservative approximate inference algorithms.
The structure of the paper is outlined as follows.
Section \ref{sec:background} describes the statistical formalism, necessary background and includes a thorough motivation for coverage.
Section \ref{sec:experiments} highlights our main results.
Section \ref{sec:discussion} presents several avenues of future research to {\bfseries enable drawing reliable scientific conclusions} with simulation-based inference. All code related to this manuscript is available at
\href{https://github.com/anonymous/anonymous}{\texttt{github.com/anonymous/anonymous}}.
%\href{https://github.com/JoeriHermans/troubles-in-paradise}{\texttt{github.com/montefiore-ai/troubles-in-paradise}}

%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, the natural sciences make decisions based on frequentist confidence intervals or Bayesian credible regions.

%Although simulation-based inference targets domain sciences, advances in the field are mainly driven from a machine learning perspective.
%The field therefore inherits the quality assessments \citep{lueckmann2021benchmarking} customary to the machine learning literature which usually involves maximizing some criterion. Despite recent developments of post hoc diagnostics to inspect the quality of likelihood-free approximations \citep{cranmer2015approximating, Brehmer:2018eca, brehmer2019mining, Hermans:2020skz, lueckmann2021benchmarking, sbc, dalmasso2020confidence}, the problem concerning \emph{scientific conclusions} based on simulation-based inference remains: \emph{can these techniques be used to drive scientific research whenever their fitting criteria are not globally optimized or the availability of data is limited?}

%{\bfseries sciences are rather concerned with
%\emph{excluding} hypotheses at some confidence level}

%As an illustration of this, a recent application consist in inferring the nature (cold or warm) and mass of dark matter through the observation of the evolution of stellar streams' density. The simulator evolves a stream and its stellar density through a stochastic iterative process though interactions with a family of dark matter subhaloes parametrized though the mass of the dark matter \arnaud{where does the nature appear?}. The iterative nature of the simulator leads to an intractable likelihood since evaluating it would require to consider all execution paths. \joeri{Rewrite}

%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, the natural {\bfseries sciences are rather concerned with
%\emph{excluding} hypotheses at some confidence level}
%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, a common concern in natural {\bfseries sciences is rather to \emph{exclude} hypotheses at some confidence level}.

%For this reason, domain scientists want guarantees to whether statistical \emph{approximations} have confidence intervals (frequentist) or credible regions (Bayesian) not smaller than they should be. In this work we adopt the Bayesian point of view, and are then concerned with not rejecting viable parameters from the credible region and incorrectly drive scientific inquiry.
%If that would \emph{not} be the case, scientists could reject viable hypotheses and incorrectly drive scientific inquiry.

%Considering the example of the inference of the nature and mass of dark matter based on the observation of a stellar streams, incorrectly inferring the nature can have a disastrous cascading effects. Those can be found in the field of particle physics where excluding warm dark matter would exclude the hypothesized sterile neutrino. \arnaud{refs} On the contrary, if cold dark matter were to be excluded, the theory for the disruptions of stellar streams would not hold.

%{\bfseries what guarantees or properties do these techniques have whenever their fitting criteria are not globally optimized or the availability of data is limited?}

% Every result and figure is annotated with \code{https://github.com/montefiore-ai/troubles-in-paradise}, linking to the code used to generate it.

%Despite recent methodological developments~\gilles{refs} and successes across various scientific use cases~\gilles{refs}, a major criticism of simulation-based inference is that the involved statistical computations are essentially not verifiable and are therefore not suitable for scientific disciplines whose primary objective is to \emph{constrain} parameters of interest, or \emph{exclude} models at a certain confidence level.

%We emphasize that algorithms should not just show high performances \arnaud{rephrase}. In the case of Bayesian posterior inference, domain scientists should also have guarantees that credible regions identified with approximate posteriors are not smaller than they should be, since rejecting parameter values compatible with the data will drive the scientific inquiry to wrong conclusions. \arnaud{this is the case with ... concrete example, gw, streams and refs}

%These concerns have led to further work focusing on improving the accuracy of inference procedures~\gilles{refs} and to the development of post hoc diagnostics to inspect the quality of their approximations~\citep{cranmer2015approximating, Brehmer:2018eca, brehmer2019mining, Hermans:2020skz, lueckmann2021benchmarking}.
%Despite these innovations, it remains unanswered what formal guarantees these techniques have whenever their approximations are not optimal, or equivalently, whenever their fitting criteria are not globally optimized.

%Theoretical characterizations of simulation-based techniques are critically needed to draw scientific conclusions reliably. 
%In this work, we study the empirical coverage of various simulation-based inference techniques over multiple benchmarks and first demonstrate that all those techniques may lead to credible regions that are too narrow with respect to the ground truth, hence leading to Type-I errors and possibly to wrong scientific conclusions. 
%We argue that model regularization constitutes a potential solution and provide a critical discussion about the ability to diagnose such pathologies. The paper is outlined as follows. \arnaud{Update paper structure} Section~\ref{sec:background} outlines the statistical formalism and the necessary background of simulation-based inference. We briefly highlight the importance of a proper diagnostic to inspect the statistical quality of the approximations. Section~\ref{sec:method} outlines our theoretical results and proposed methodology, supported by experimental validation in Section~\ref{sec:experiments}.
\section{Background}
\label{sec:background}

\subsection{Statistical formalism}
\label{sec:statistical_formalism}
We evaluate posterior estimators that produce approximations $\hat{p}(\vtheta\vert\vx)$ with the following semantics.

{\bf Target parameters} $\vtheta$ denote the parameters of interest of a simulation model, and are sometimes referred to as \emph{free} or \emph{model} parameters. The precise definition of $\vtheta$ depends on the problem setting. We make the reasonable assumption that the prior $p(\vtheta)$ is a known and tractable quantity.

The {\bf observable} $\vx$ denotes the synthetic realizations of the simulator. Observed data $\vx_o$ is the observable we would like to do inference on, under the assumption that the simulation model is correctly specified.

The {\bf likelihood} model $p(\vx\vert\vtheta)$ implicitly defined by the simulator's computer code. While we cannot evaluate the density $p(\vx\vert\vtheta)$, we \emph{can} simulate samples.

The {\bf ground truth} $\vtheta^*$ specified to the simulation model whose forward evaluation produced the observable $\vx_o$, i.e., $\vx_o\sim p(\vx\vert\vtheta=\vtheta^*)$.

The {\bf credible region} is a space $\Theta$ within the target parameter domain that satisfies
\begin{equation}
    \int_\Theta p(\vtheta\vert\vx=\vx_o) \d{\vtheta} = 1 - \alpha
\end{equation}
for some observable $\vx_o$ and confidence coefficient $1 - \alpha$.
Because many such regions exist, we compute the credible region with the \emph{smallest} volume. In the literature this credible region is known as 
the \emph{highest posterior density region} \citep{box2011bayesian,hyndman1996computing}.

%which can either be the posterior itself. Or the likelihood-to-evidence ratio 
%$$r(x\vert\vartheta) = \frac{p(x \vert \vartheta)}{p(x)}.$$ 
%Through approximations $\hat{r}(x\vert\vartheta)$, evaluating estimates of the posterior density function amount to computing the product of the \emph{tractable} prior probability $p(\vartheta)$ and the estimated likelihood-to-evidence ratio $\hat{r}(x\vert\vartheta)$. An unormalized approximate of the posterior can also be recovered from a surrogate for the likelihood by multiplying it to the prior probability.

%\subsection{Likelihood-free inference methods}
\subsection{Statistical quality assessment}
%The work of \citet{lueckmann2021benchmarking} benchmarks common simulation-based
%techniques on various metrics. Although the benchmarks are done very thoroughly with respect to the \emph{selected} metrics, 
%there are issues regarding their \emph{applicability}.

\begin{figure}[b!]
    \centering
    \includegraphics[width=\linewidth]{figures/auc-deceitful.pdf}
    \caption{A classifier-based metric measures the divergence between posterior approximations and a ground truth by means of evaluating the classifier's discriminative performance through Area Under the Receiver Operating Characteristics curve (\textsc{auroc}). In this case, the metric argues that both the conservative and overconfident approximations are equally accurate since the metric yields \textsc{auroc} = 0.7 for both approximations. From an inference perspective however, the conservative approximation is clearly more suitable because it produces credible regions larger than they should be.}
    \label{fig:auc_deceitful}
\end{figure}
The main problem with metrics such as the Classifier Two-sample Test \citep{lehmann2006testing,lopez2016revisiting} or Maximum Mean Discrepancy \citep{gretton2012kernel,bengio2013bounding,dziugaite2015training} is that they assess \emph{accuracy} or \emph{closeness} of an approximation through a divergence with respect to a posterior that is intractable in practice.
Even if such evaluations would hypothetically be possible,
there are no criteria to what constitutes an \emph{acceptable} estimator.
%for scientific use-cases.
In addition, it is not possible to know for certain whether the classifier or kernel used to measure the diverge are sufficiently expressive to detect differences between the approximation and said posterior.

To clarify these points, consider the demonstration in Figure \ref{fig:auc_deceitful}.
A binary classifier is trained to discriminate between samples from a posterior approximation and the true posterior.
The discriminative performance of the classifier is expressed through Area Under the Receiver Operating Characteristics curve (\textsc{auroc}) and serves as a measure for divergence between both densities. An \textsc{auroc} = 0.5 suggests an approximation that is indistinguishable from the true posterior, while \textsc{auroc} = 1.0 implies that both densities do not overlap.
Although both approximations in our demonstration are equally accurate according to the \textsc{auroc}, the \emph{overconfident} approximation demonstrates the potential trust crisis in simulation-based inference:
producing credible regions that are biased or smaller than they should be, leading to erroneous scientific conclusions. 
For this reason, we take the position that posterior approximations should, irrespective of the available simulation budget, produce inflated credible regions and do not have to closely match the true posterior to draw meaningful inferences.

Instead of measuring accuracy of approximations with respect to an intractable posterior, this work directly probes
the quality of credible regions through \emph{coverage}: a quantity that can be estimated in practice and has a criterion to determine acceptable approximations.
\begin{definition}
The {\bfseries coverage probability} of a posterior estimator at a confidence coefficient $1 - \alpha$ is
\begin{equation}
    \int_{\vtheta}\int_{\vx} p(\vtheta,\vx)~\mathbb{1}\left[\vtheta \in \Theta_{\hat{p}(\vtheta|\vx = \vx)}(1 - \alpha)\right]~\d\vtheta\d\vx,
\end{equation}
where the function
$\Theta_{p(\vtheta\vert\vx)}(1 - \alpha)$ yields the $1 - \alpha$ highest posterior density region
of $\hat{p}(\vtheta\vert\vx)$.
%\begin{equation}
%\mathbb{E}_{(\vtheta^*, \vx_o) \sim p(\vtheta, \vx)} \left\{ \begin{array}{ll}
%    1 & \text{if } \vtheta^* \in \Theta_{\hat{p}(\vtheta|\vx = \vx_o)}(1 - \alpha) \\
%    0 & \text{otherwise}
%\end{array} \right..
%\end{equation}
\end{definition}
\begin{definition}
The {\bfseries empirical coverage probability} of a posterior estimator at a confidence coefficient $1 - \alpha$ given a set of $n$ i.i.d. samples $(\vtheta^*,\vx)\sim p(\vtheta,\vx)$
is
\begin{equation}
\frac{1}{n} \sum_{i=1}^n ~\mathbb{1}\left[\vtheta^*_i \in \Theta_{\hat{p}(\vtheta|\vx = \vx_i)}(1 - \alpha)\right].
\end{equation}
\end{definition}
\begin{definition}
The {\bfseries nominal coverage probability} is the coverage probability of the true posterior and is equal to the known confidence level $(1 - \alpha)\cdot 100\%$.
\end{definition}
\begin{definition}
A posterior estimator is deemed acceptable if it {\bfseries has coverage} at the confidence level of interest, i.e., whenever the empirical coverage probability is {\bfseries larger or equal} to the nominal coverage probability.
\end{definition}
\begin{definition}
A {\bfseries conservative estimator} is an estimator that has coverage for {\bfseries all} confidence levels.
\end{definition}
% \begin{definition}
% The {empirical \bfseries coverage probability} of a posterior estimator at a confidence level $1 - \alpha$ given a set of $n$ i.i.d. samples $(\vtheta^*,\vx)\sim p(\vtheta,\vx)$
% is
% \begin{equation}
% \frac{1}{n} \sum_{i=1}^n \left\{ \begin{array}{ll}
%     1 & \text{if } \vtheta^*_i \in \Theta_i \\
%     0 & \text{otherwise}
% \end{array} \right.,
% \end{equation}
% where $\Theta_i$ is the credible region computed through the posterior approximation $\hat{p}(\vtheta\vert\vx=\vx_i)$ considering that $\vx_i \sim p(\vx\vert\vtheta = \vtheta^*_i)$.
% \end{definition}
% \begin{definition}
% The {\bfseries nominal coverage probability} is effectively equal to the confidence level.
% \end{definition}
% \begin{definition}
% An estimator is deemed acceptable if it {\bfseries has coverage} at the confidence level of interest. That is, whenever the empirical coverage probability is {\bfseries larger or equal} to the nominal coverage probability.
% \end{definition}
% \begin{definition}
% A {\bfseries conservative estimator} is an estimator that has coverage for {\bfseries all} confidence levels.
% \end{definition}
Although coverage is a necessary metric to assess conservativeness, it is limited in its ability to determine the information gain a posterior (approximation) has over its prior. To clarify this point, consider an estimator whose posteriors are identical to the prior. In this case, there is no gain in information and the empirical coverage probability is equal to the nominal coverage probability. For this reason, a complete analysis should be complemented with measures such as the mutual information or expected information gain $\mathbb{E}_{p(\vtheta,\vx)}\left[\log p(\vtheta\vert\vx) - \log p(\vtheta)\right]$.
This work however is concerned with {\bfseries conservative inference} and will therefore limit the analysis to the evaluation of coverage. Finally, it should be noted that coverage is a statement about the credible regions in expectation. Coverage does not make any statement about the quality of a single posterior.

\section{Experimental observations}
\label{sec:experiments}
This section covers our main contribution: the collection of empirical evidence to determine whether approaches in simulation-based inference are conservative by nature. 
We are particularly interested in determining \emph{if} certain approaches should be
favoured over others. We do so by measuring the coverage of estimators attained by these approaches across a broad range of hyperparameters and benchmarks of varied complexity, including two \emph{real} problems from the field of astronomy.
As in real use-cases, the true posteriors associated with these benchmarks are unknown.
Hyperparameters are listed in Appendix \ref{appendix:hyperparameters}.
\subsection{Methods}
\label{sec:methods}
We make the distinction between two paradigms.
Non-amortized approaches are designed to approximate a \emph{single} posterior, while amortized methods aim to learn a general purpose estimator that attempts to approximate \emph{all} posteriors supported by the prior. 
\subsubsection{Amortized}
%from  posterior $p(\vartheta|x_0)$ for an observable $x_0$. Candidates parameters $\vartheta_i$ are first sampled from the prior, $p(\vartheta)$. Those parameters are then used along with the simulator to produce observations $x_i$. The candidate parameters that have produced the closest observations to the target observation $x_0$ according to some distance metric are kept and considered samples from the posterior, $p(\vartheta|x_0)$. \arnaud{add details?: norm 2 distance + quantile 0.01 with at least 100 samples?}  
%Sequential Monte-Carlo ABC (SMC-ABC) \citep{10.1093/bioinformatics/btp619, sisson2007sequential, beaumont2009adaptive} iteratively update a set of particules to match the posterior distribution. At each iteration, candidate parameters that produced the highest distance are discarded and new candidates are generated by adding a perturbation to the remaining candidates. \arnaud{double check that this is correct}
{\bf Neural Posterior Estimation} (\npe) is concerned with directly learning an amortized estimator $\hat{p}_\psi(\vtheta\vert \vx)$ to the posterior with normalizing flows. Normalizing flows define a class of probability distributions $p_\psi(\cdot)$ built from neural network based bijective transformations \citep{dinh2014nice,dinh2016density} parameterized by $\psi$ and are usually optimized via
$\argmin_\psi \mathbb{E}_{p(\vx)} \left[\textsc{kl}(p(\vtheta|\vx)~\vert\vert ~\hat{p}_\psi(\vtheta|\vx)\right]$,
which is equivalent to $\argmax_\psi \mathbb{E}_{p(\vtheta,\vx)}\left[\log \hat{p}_\psi(\vtheta|\vx)\right]$.
Once trained, the density of the modeled distribution can easily be evaluated \emph{and} sampled from.

{\bf Neural Ratio Estimation} (\nre) is an established approach in the simulation-based inference literature both from a frequentist \citep{cranmer2015approximating} and Bayesian \citep{thomas2016likelihood,2019arXiv190304057H} perspective. In a Bayesian analysis, 
an amortized estimator $\hat{r}(\vx\vert\vtheta)$
of the \emph{intractable} likelihood-to-evidence ratio $r(\vx\vert\vtheta)$ can be learned by training a binary discriminator $\hat{d}(\vtheta,\vx)$ with inputs $\vtheta$ and $\vx$ to distinguish between samples of the
joint $p(\vtheta,\vx)$ with class label 1 and samples of the product of marginals $p(\vtheta)p(\vx)$ with class label 0 using a criterion such
as the binary cross entropy. Similar to the density-ratio trick \citep{sugiyama2012density,goodfellow2014generative,cranmer2015approximating,2019arXiv190304057H}, the Bayes optimal discriminator $d(\vtheta,\vx)$ models
\begin{align}
  \frac{p(\vtheta, \vx)}{p(\vtheta,\vx) + p(\vtheta)p(\vx)} = \sigmoid\left(\log\frac{p(\vtheta,\vx)}{p(\vtheta)p(\vx)}\right),
\end{align}
where $\sigmoid(\cdot)$ is the sigmoid function.
Given a target parameter $\vtheta$ and observable $\vx$ supported by $p(\vtheta)$ and $p(\vx)$ respectively,
the learned discriminator $\hat{d}(\vtheta,\vx)$ approximates the log likelihood-to-evidence ratio $\log r(\vx\vert\vtheta)$ through the logit function $\logit(\cdot)$ because
\begin{align}
  \log \hat{r}(\vx\vert\vtheta) &= \logit\left(\hat{d}(\vtheta,\vx)\right) = \log\frac{\hat{d}(\vtheta,\vx)}{1 - \hat{d}(\vtheta,\vx)}\\ 
  &\approx \log\frac{p(\vtheta, \vx)}{p(\vtheta)p(\vx)} = \log\frac{p(\vx\vert\vtheta)}{p(\vx)}.
\end{align}
The log posterior density function is approximated as $\log \hat{p}(\vtheta\vert\vx) = \log p(\vtheta) + \log \hat{r}(\vx\vert\vtheta)$.

{\bf Ensembles} An ensemble model \emph{averages} the approximated posteriors of $n$ separately trained posterior estimators. While this formulation is natural for \textsc{npe}, averaging likelihood-to-evidence ratios is equivalent, because
\begin{equation}
    \frac{p(\vtheta)}{n} \sum_{i=1}^n \hat{r}_i(\vx \vert \vtheta) = \frac{1}{n}\sum_{i=1}^n \hat{p}_i(\vtheta \vert \vx).
\end{equation}
\subsubsection{Non-amortized}
Rejection {\bf Approximate Bayesian Computation} \textsc{(abc)} \citep{rubin1984,pritchard1999population}
numerically estimates a \emph{single} posterior by collecting samples $\vtheta\sim p(\vtheta)$ whenever
$\vx\sim p(\vx\vert\vtheta)$ is \emph{similar} to $\vx_o$. Similarity is expressed by means of a \emph{distance function} $\rho$. For high-dimensional observables, the probability of simulating an observable $\vx$ such that $\vx = \vx_o$ is extremely small. For this reason, \textsc{abc} uses a \emph{summary statistic} $s$ and an \emph{acceptance threshold} $\epsilon$. Using these components, \textsc{abc} accepts samples into the approximate posterior whenever $\rho(s(\vx),s(\vx_o))\leq\epsilon$. In our experiments we use the identity function as a sufficient summary statistic. Finally, we emphasize that 
\textsc{abc} approximations are \emph{only exact} whenever the summary statistic is sufficient \emph{and} the acceptance threshold $\epsilon$ tends to 0 \citep{sisson2018overview}.
% Note that
% amortized estimates of the likelihood-to-evidence ratio $r(x\vert\vartheta)$ can be computed through $\hat{p}_\psi(\vartheta\vert x)$ because
% $\log r(x\vert\vartheta) \approx \log \hat{p}_\psi(\vartheta\vert x) - \log p(\vartheta)$. Therefore, the binary discriminator $\hat{d}(\vartheta,x)\triangleq\sigmoid(\log\hat{p}_\psi(\vartheta\vert x) - \log p(\vartheta))$ enables $\hat{p}_\psi(\vartheta,x)$ to be {\bf learned by minimizing
% the binary cross entropy criterion} presented above. All flow-based estimators in this work are optimized using the aforementioned criterion unless stated otherwise.
% \joeri{We can remove this right? Yes my bad}
% Once trained, we can sample new data points from the modeled distribution as well as evaluate the density of new data points. We highlight two possibilities for building an approximate amortized posterior $p_\psi(\vartheta|x)$ with NFs. First, by direct minimization of the \textsc{kl} divergence between the approximate posterior and the actual posterior,
% \begin{align}
%     \psi^* &= \argmin_\psi \mathbb{E}_{p(x)}\left[\textsc{kl}(p(\vartheta|x)~\vert\vert ~p_\psi(\vartheta|x)\right] = \argmin_\psi \mathbb{E}_{p(x)}\mathbb{E}_{p(\vartheta|x)}\left[\log\frac{ p(\vartheta|x)}{p_\psi(\vartheta|x)}\right]\\
%     &= \argmax_\psi \mathbb{E}_{p(\vartheta,x)}\left[\log p_\psi(\vartheta|x)\right].
% \end{align}
% \antoine{Say it is equivalent to MLE. (amortized over posteriors)}
% The second option is to define the NF likelihood-to-evidence ratio as 
% \begin{align}
%     r_\psi(x|\vartheta) := \frac{p_\psi(\vartheta|x)}{p(\vartheta)},
% \end{align}
% and to train it as a classifier-based amortized ratio estimator.
% \antoine{Add the two training methods have the same optimum but the second may be tuned to be blablabla as shown later}
% \joeri{My take below?}

%{\bfseries Sequential methods} aim at estimating the posterior for a specific observable $x_o$ by dedicating the simulation budget to iteratively improve an approximation.
%These methods alternate between a training and a simulation phase, the latter being designed to take \emph{current} knowledge into account such that subsequent simulation parameters $\vartheta$ are expected to produce observables $x$ closer to $x_o$ compared to previous iterations.

Sequential methods aim to approximate a single posterior by \emph{iteratively} improving a posterior approximation. These methods alternate between a simulation and exploitation phase. The latter being designed to take \emph{current} knowledge into account such that subsequent simulations can be focused on parameters that are more likely to produce observables $x$ similar to $x_o$.

{\bfseries Sequential Monte-Carlo ABC} (\textsc{smc-abc}) \citep{10.1093/bioinformatics/btp619, sisson2007sequential, beaumont2009adaptive}
iteratively updates a set of proposal states to match the posterior distribution. At each iteration, accepted proposals are ranked by distance. The rankings determine whether a proposal is propagated to the next iteration. New candidate proposals are generated by perturbing the selected ranked proposals.

{\bfseries Sequential Neural Posterior Estimation} (\snpe) \citep{papamakarios2016fast, lueckmann2017flexible, greenberg2019automatic} directly models the posterior.
Our evaluations will specifically use the \textsc{snpe-c} \citep{greenberg2019automatic} variant.

{\bfseries Sequential Neural Likelihood} (\textsc{snl}) \citep{papamakarios2019sequential} models the likelihood $p(\vx|\vtheta)$. A numerical approximation of the posterior is obtained by plugging the learned likelihood estimator into a Markov Chain Monte Carlo (\textsc{mcmc}) sampler as a surrogate likelihood.

{\bfseries Sequential Neural Ratio Estimator} (\snre) \citep{2019arXiv190304057H,durkan2020contrastive} iteratively improves the modelled likelihood-to-evidence ratio.
\subsection{Benchmarks}
Our evaluations consider 7 benchmarks, ranging from toy problems to real applications in astronomy. Appendix \ref{appendix:simulation_times} lists the expected wall-clock time to generate 1000 simulations on a single CPU core.

The \emph{SLCP} simulator models a fictive problem with 5 parameters. The observable $\vx$ is composed of 8 scalars which represent the 2D-coordinates of 4 points. 
The coordinate of every point is sampled from the same multivariate Gaussian whose mean and covariance matrix are the parameters $\vtheta$. We consider a simplified version of the original task \citep{papamakarios2019sequential} by inferring the marginal posterior density of 2 of those parameters. In contrast to its original formulation, the likelihood is not tractable due to the marginalization.

The \emph{Weinberg} problem \citep{weinberg} concerns a simulation of high energy particle collisions $e^+e^- \to \mu^+ \mu^-$. The angular distributions of the particles can be used to measure the Weinberg angle $\vx$
in the standard model of particle physics. From the scattering angle, we are interested in inferring Fermi's constant $\vtheta$.

The \emph{Spatial SIR} model generates a grid-world $\vx$ of susceptible,
infected, and recovered individuals. This information is encoded in 3
channels. Based on the initial state of $\vx$ and the infection and recovery rate $\vtheta$,
the model describes the evolution of an infection through this grid-like world.
The disease spreads spatially.

Originally introduced by \citet{papamakarios2019sequential}, \emph{M/G/1} models a processing and arrival queue. The problem is
described by 3 parameters $\vtheta$ that influence the time it takes to serve a customer, and the time between their arrivals. The observable $\vx$ is composed of 5 equally spaced quantiles of inter-departure times.

The \emph{Lotka-Volterra} population model \citep{lotka,volterra1926fluctuations} describes a process of interactions between a predator and a prey species. The model is conditioned by 4 parameters $\vtheta$ which influence the reproduction and mortality rate of the predator and prey species. We infer the marginal posterior of the 2 predator's parameters. Our implementation, described by a Markov process, generates 2 time-series of 1001 samples representing the evolution of the prey and predator populations over time.

Stellar \emph{Streams} form due to the disruption of spherically packed clusters of stars by the Milky Way. Because of their distance from the galactic center and other visible matter, \emph{distant} stellar streams are considered to be ideal probes to detect gravitational interactions with dark matter. The simulation model \citep{bovy2015galpy,banik2018probing,Hermans:2020skz} evolves the stellar density $\vx$ of a stream over several billion years, while perturbing the stream over its evolution through interactions with dark matter subhaloes parameterized through the dark matter particle mass $\vtheta$.

\emph{Gravitational Waves (GW)} are ripples in space-time emitted during events such as the collision of two black-holes. They can be detected through interferometry $\vx$ and convey information about the celestial bodies, unlocking a new way to study the universe. We consider the task of inferring the masses $\vtheta$ of two black-holes colliding through the observation of the gravitational wave as measured by \textsc{ligo}'s dual detectors \citep{lalsuite,Biwer:2018osg}.

\subsection{Setup}
Our evaluations consider simulation budgets ranging from $2^{10}$ up to $2^{17}$ samples and confidence levels from 0.05 up to 0.95. Within the \emph{amortized} setting
we train, for every simulation budget, 5 posterior estimators for 100 epochs. The empirical coverage probability is 
computed on at least 5,000 unseen samples from the joint $p(\vtheta,\vx)$ and for all confidence levels under consideration.
In addition, we repeat the coverage evaluation for ensembles of 5 estimators as well.

Special care for \emph{non-amortized} approaches is necessary because they only approximate a \emph{single} posterior and can therefore not evaluate coverage.
Our experiments estimate coverage of these methods \emph{by proxy} by repeating the inference procedure on 300 distinct observables for a given simulation budget (2100 times per method per benchmark).
The empirical coverage probabilities are subsequently estimated using the 300 approximated posteriors. 
Our experiments with \textsc{npe}, \textsc{snpe}, \textsc{snl}, \textsc{snre}, \textsc{rej-abc} and \textsc{smc-abc} rely on \texttt{sbi}'s \citep{sbi} reference implementation, while we use a custom implementation for \textsc{nre}.

{\bfseries Computational cost} We would like to emphasize the computational requirements necessary to generate our main contribution: the experimental observations, whose generation took months on several computer clusters. The bulk of the cost was associated with the repeated optimization procedure of non-amortized methods and the constant resampling of the simulator.

\subsection{Results}
\begin{figure*}[h!]
    \includegraphics[width=\textwidth]{figures/coverage_multi.pdf}
    \caption{Evolution of the coverage w.r.t simulation budget. A perfectly calibrated posterior has an empirical coverage probability equal to the nominal coverage probability and produces a diagonal line. Conservative estimators on the other hand produce curves above the diagonal and overconfident models underneath. All algorithms can lead to non-conservative estimators, this pathology tends to be accentuated for small simulation budgets and non-amortized methods.
    Finally, the intractable results indicate that the computational requirements did not allow for a coverage analysis. In the case of \textsc{snl}, this was mostly due to the high dimensional observables. We did not train an embedding network as that is outside of the scope of this work. For the astronomy applications, the simulation model was simply too expensive to reasonable evaluate coverage for non-amortized methods.
    }
    \label{fig:all_coverage_levels}
\end{figure*}
\begin{figure*}[h!]
    %\includegraphics[width=\textwidth]{figures/coverage_multi_ensemble.pdf}
    \includegraphics[width=\textwidth]{figures/coverage_multi_ensemble_with_bagging.pdf}
    \caption{Analysis of coverage between ensemble and individual models w.r.t various simulation budgets. The blue line represents the mean coverage of individual models over 5 runs, the shaded area represents its standard deviation. The black line represents the coverage of a single ensemble composed of 5 models. We observe that ensembles consistently have a higher empirical coverage probability compared to the average individual model. A similar effect is not always observed with bagging, indicated by the red line. Ensembles are only considered on amortized approached due to computational requirements inherent to non-amortized approaches.}
    \label{fig:coverage_ensemble}
\end{figure*}
Figures \ref{fig:all_coverage_levels} and \ref{fig:coverage_ensemble} highlight our main results. Through these plots we can directly assess the \emph{conservativeness} at a given confidence level and simulation budget. The figures should be interpreted as follows: a \emph{perfectly calibrated} posterior has an empirical coverage probability equal to the nominal coverage probability and therefore the known confidence level. Plotting this relation produces a diagonal line. Conservative estimators on the other hand produce curves above the diagonal and overconfident models underneath.
The plots highlight an unsettling observation: {\bfseries all} benchmarked approaches produce non-conservative posterior approximations. In general, this pathology is especially prominent in non-amortized approaches with a small simulation budget. A regime they have been specifically designed for. However, a large simulation budget does not guarantee conservativeness either.

In sequential approaches, this behaviour can be explained by the alternating exploitation and simulation phase. One potential failure mode
is that a non-conservative posterior approximation at a previous iteration forces the next simulation phase to not produce observables
that should in fact be associated with a higher posterior density, causing the estimator to be more non-conservative at each iteration.
Extreme cases were observed in the form of posterior approximations that have density \emph{outside} of the support of the prior.

Despite the fact that all \textsc{abc} approaches use a sufficient summary statistic (the identity function), our results demonstrate that this alone is no guarantee for conservative posterior approximations. In fact,
using a sufficient summary statistic with $\epsilon > 0$ does not always, as demonstrated, correspond to conservative approximations.
In such cases, \textsc{abc} accepts
samples with larger distances, permitting the procedure to shift the mass of the approximated posterior elsewhere. In addition, a limited number of posterior samples can negatively affect the quality of the credible regions, e.g., when approximating the posterior density function with kernel density estimation.
Both cases cause the observed behaviour. Scientific applications should therefore be cautious when applying \textsc{abc}. Even though a handcrafted, albeit sufficient, summary statistic provides some insight into the approximated posterior, there are no guarantees that \textsc{abc} approximations are conservative whenever $\epsilon > 0$.

% In Figure \ref{fig:coverage_ensemble} we observe that the empirical coverage probability of the ensemble models is consistently larger than the empirical coverage probability of the expected individual estimator. Individual estimators only captures aleatoric uncertainty, i.e., uncertainty that is linked to stochasticity of the data generation procedure. Ensembles are expected to also capture part of the epistemic uncertainty, i.e., uncertainty issued by the lack of knowledge. In particular, ensembles capture the uncertainty related to the training procedure. This added uncertainty results in a larger credible region increasing the empirical coverage probability. Although ensembles take part of the epistemic uncertainty into account, they can still produce non-conservative posteriors. 
% Current applications of simulation-based inference can therefore rely on ensembling to build increasingly conservative posterior estimators.
% It should be noted however that bagging does not yield a similar effect.
% As shown in Appendix \ref{sec:additional_results}, a positive effect with respect to ensemble size is observed.
In Figure \ref{fig:coverage_ensemble} we observe that the empirical coverage probability of ensemble models is consistently larger than the empirical coverage probability of the expected individual posterior estimator. Current applications of simulation-based inference can therefore rely on ensembling to build increasingly conservative posterior estimators. However, the ensemble model can still be non-conservative. We hypothesize that the increase in coverage is linked to the added uncertainty captured by the ensemble model, leading to inflated credible regions. In fact, individual estimators only captures aleatoric uncertainty, i.e., uncertainty that is linked to stochasticity of the data generation procedure, while an ensemble is expected to capture \emph{part} of the epistemic uncertainty as well, i.e., uncertainty issued by the lack of knowledge. Surprisingly, we find that ensembles built using bagging do not always produce higher coverage than individual models while they should also capture part of the epistemic uncertainty. Although a deeper understanding of this effect would be required, this behaviour could be explained by the fact that bagging reduces the effective dataset size used to train each member of the ensemble. As shown in Appendix \ref{sec:additional_results}, a positive effect with respect to ensemble size is observed.

Not evident from Figures \ref{fig:all_coverage_levels} and \ref{fig:coverage_ensemble}
are the computational consequences of a necessary coverage analysis on non-amortized methods.
Although the figures mention a certain simulation budget, the \emph{total} number of simulations for non-amortized methods should be multiplied by the number of approximated posteriors (300) to estimate coverage, highlighting the simulation cost associated with diagnosing non-amortized approaches.
This observation issue is not limited to coverage. Simulation-Based Calibration (\textsc{sbc}) \citep{sbc} relies on samples of arbitrary posterior approximations.
Diagnosing non-amortized estimators with \textsc{sbc} therefore 
requires a similar approach as we have taken in our coverage analyses.
In fact, \citet{lueckmann2021benchmarking} also mention that \textsc{sbc} is computationally prohibitive for non-amortized (sequential) approaches and therefore restrain from evaluating it.

Our results illustrate a clear distinction between the amortized and non-amortized paradigms. Amortized methods do not require retraining or new simulations to determine the empirical coverage probability of a posterior estimator, while non-amortized methods do.
Moreover, a coverage analysis of non-amortized approaches only measures the quality of the training procedure. In contrast to amortized approaches, where the posterior estimator is diagnosed.
This has severe
implications on the applicability of non-amortized methods, because their reliability cannot be practically determined. In addition, non-amortized approaches have to repeat the approximation procedure whenever architectural or hyperparameter changes are made, while amortized methods reuse previously simulated datasets. In particular, sequential methods cannot do this as new simulations depend on the posterior approximation at a previous state. This is often overlooked in studies on simulation efficiency and raises questions about whether sequential approaches should still be considered simulation efficient over their amortized counterparts. Especially because our results indicate that for a given simulation budget, amortized approaches produce trustworthier posterior approximations in expectation.

All of the above leads us to conclude that \emph{currently}, amortization should be favoured over non-amortized approaches because they are tedious to diagnose. Remarkably, our results suggest that even for small simulation budgets amortized methods do in fact, on average, produce more conservative posterior estimators compared to non-amortized methods.
A striking result, given that sequential methods dedicate the available simulation budget to accurately approximate a single posterior. No clear distinction between \textsc{nre} and \textsc{npe} was observed. Although interestingly, ensembling leads to significant improvements with respect to coverage.

\medskip

\begin{custombox}
{\bfseries Observation 1} All benchmarked algorithms produce non-conservative posterior approximations. This pathology tends to be accentuated when using a small simulation-budget in both amortized and non-amortized approaches.

\medskip

{\bfseries Observation 2} For a given simulation budget, amortized approaches have the tendency to be more conservative than non-amortized approaches.

\medskip

{\bfseries Observation 3} The empirical coverage probability of an ensemble model is larger than the expected individual model. The ensemble size positively affects the empirical coverage probability as well.

\medskip

{\bfseries Observation 4} Amortized methods are not subordinate with respect to the simulation-efficiency of non-amortized sequential methods, especially when taking hyper-parameter tuning and the evaluation of the coverage diagnostic into account.
\end{custombox}
\section{Discussion}
\label{sec:discussion}
%This work establishes that \textsc{(s)npe}, \textsc{(s)nre}, \textsc{snl} and various forms of \textsc{abc} can produce non-conservative posterior approximations. Performing a coverage-like diagnostic is therefore necessary before applying the learned posterior estimator.
Assessing the \emph{correctness} of posterior approximations is not restricted to simulation-based inference specifically, the question recurs in all of approximate Bayesian inference. 
In particular, the \textsc{mcmc} literature deals with this exact same problem in the form of determining whether a set of Markov chain samples have \emph{converged} to the target distribution \citep{lin2014integrated,hogg2018data}. 
Although empirical diagnostic tools exist \citep{geweke1991evaluating,gelman1992inference,raftery1991many,dixit2017mcmc},
there is as no clear solution to determine covergence with absolute certainty \citep{dixit2018developments,roy2020convergence}, even though the evaluation of the likelihood model is tractable.
Nevertheless, this has not prevented practitioners from applying \textsc{mcmc}, especially when considering the theoretical guarantees that come with the samplers. For this reason, we are of the opinion that theoretical and methodological advances in simulation-based inference (beyond global optima) will improve the reliability of simulation-based inference and promote its applibability in the sciences.

Recently, \citet{dalmasso2021likelihood} have explored this direction in the frequentist setting by introducing an algorithm for the construction of confidence intervals that are guaranteed to have perfect coverage in the infinite sample setting regardless of the quality of the statistic used. In the finite sample setting, they provide a theoretical bound on the approximation error. 
However, this bound is an absolute value and does not ensure conservativeness for a given simulation budget.

Our results show that ensembling produce increasingly conservative posteriors. Ensembles and model averaging in general, including the field of Bayesian deep learning, constitute a promising research direction. A theoretical understanding of these frameworks in the context of simulation-based inference would further strengthen their applicability.
% Our results show that ensembling constitutes a promising research direction. A theoretical understanding for the observation that ensembles produce increasingly conservative posteriors would further strengthen their applicability. In addition, the idea of capturing epistemic uncertainty with ensembles could further be extended using the \emph{Bayesian Deep Learning} framework, which attempts to model an approximate posterior over the weights of a neural network given the available data. The Bayesian framework assigns a clear interpretation to those uncertainties because they arise from the prior and likelihood. On the other hand, the uncertainty in ensembles arise from the stochasticity during training.
% In addition, the idea of capturing epistemic uncertainty with ensembles could further be extended using the \emph{Bayesian Deep Learning} framework, which attempts to model an approximate posterior over the weights of a neural network given the available data. In the likelihood-free setting, this data would be issued from the simulator. The posterior for a given observable would subsequently be obtained by marginalizing the posterior over the available weights. As with ensembles, the posterior over the weights takes epistemic uncertainty into account, which is the uncertainty issued by the lack of knowledge. The Bayesian framework assigns a clear interpretation to those uncertainties because they arise from the prior and likelihood. The uncertainty in ensembles on the other hand arise from the stochasticity in the training procedure.

Finally, despite that the benchmarked algorithms recover the true posterior under specific optimal conditions, it is generally not possible to know whether those conditions are satisfied in practice.
The study of objective functions that force posterior estimators to be conservative, regardless of whether their fitting criteria have been globally minimized, is therefore worth exploring. However, it is not clear as of yet on how to define and encode conservativeness in objective functions. Nevertheless, such objective functions would establish formal guarantees and strengthen the reliability of posterior estimators regardless of the available simulation budget.

\subsubsection*{Acknowledgements}
Antoine Wehenkel, Arnaud Delaunoy, and Joeri Hermans would like to thank the National Fund for Scientific Research (F.R.S.-FNRS) for their scholarships.
Gilles Louppe is recipient of the ULiège - NRB Chair on Big Data and is thankful for the support of the NRB. Computational resources have been provided by the Consortium des Équipements de Calcul Intensif (CÉCI), funded by the National Fund for Scientific Research (F.R.S.-FNRS) under Grant No. 2.5020.11 and by the Walloon Region.

\bibliographystyle{plainnat}
\bibliography{main}

% Appendix
\FloatBarrier
\newpage
\appendix

\onecolumn
\section*{Appendix}
\label{appendix}

\section{Expected simulation times}
\label{appendix:simulation_times}
\begin{table}[h!]
    \centering
    \begin{tabular}{lllllll}
        \toprule
        SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        $0.22\pm 0.002$ & $0.20\pm 0.002$ & $0.20\pm 0.002$ & $19.08\pm 0.964$ & $9.18\pm 0.280$ & $545.13\pm 23.631$ & $39,369 \pm 584.43$ \\ 
        \bottomrule
    \end{tabular}
    \caption{Expected simulation time to produce 1000 simulations for all benchmark problems on a single CPU core. The expected time and standard deviation is reported in seconds.}
    \label{tab:simulation_times}
\end{table}

\section{Architectures \& hyperparameters}
\label{appendix:hyperparameters}
In this section we describe the neural architectures and hyperparameters associated with our experiments. Our descriptions are complemented with the actual number of coverage evaluations. As evident from the tables describing both amortized and non-amortized approaches, the number of coverage evaluations for amortized approaches is substantially larger. It should be noted that, a coverage analysis consisting of 300 posteriors of the non-amortized approaches took \emph{months} on these relatively simple problems. While for the amortized methods, a coverage analysis of 100,000 samples was a matter of hours to a few days depending on the dimensionality of $\vtheta$.

\subsection{Amortized}
\subsubsection{Neural Posterior Estimation}
The MLP embeddings are 3 layer MLP's with 64 hidden units and a final latent space of 10, which is fed to the normalizing flow.
The CNN architecture in the Gravitational Waves benchmark consists of a 13-layer deep convolutional head of 1D convolutions with a dilation factor of $2^d$. Where $d$ corresponds to the depth of the convolutional head. The SELU \citep{selu} function is used as an activation function.
\begin{table}[h!]
    \centering
    \begin{tabular}{llllllll}
        \toprule
        & SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        \emph{Embedding} & MLP & MLP & MLP & MLP & MLP & CNN & MLP \\ 
        \emph{Batch-size} & 128 & 128 & 128 & 128 & 128 & 64 & 128 \\
        \emph{Coverage samples individual} & 100,000 & 5,000 & 100,000 & 100,000 & 100,000 & 10,000 & 100,000 \\
        \emph{Coverage samples ensemble} & 20,000 & 5,000 & 20,000 & 20,000 & 20,000 & 5,000 & 20,000 \\
        \emph{Epochs} & 100 & 100 & 100 & 100 & 100 & 100 & 100 \\
        \emph{Model} & NSF & NSF & NSF & NSF & NSF & NSF & NSF \\
        \emph{Transforms} & 3 & 3 & 1 & 3 & 3 & 3 & 3 \\
        \emph{Learning-rate} & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 \\
        \bottomrule
    \end{tabular}
    \caption{Architectures and hyperparameters associated with Neural Posterior Estimation.}
    \label{tab:npe_hyperparameters}
\end{table}

\subsubsection{Neural Ratio Estimation}
Our experiments use the \textsc{adamw} \citep{adam,adamw} optimizer. Accross all benchmarks, the MLP architectures constitute of 3 hidden layers with 128 units and SELU \citep{selu} activations. The Gravitational Waves benchmark uses the same convolutional architecture as in \textsc{npe}. The resulting embedding is flattened and fed to a MLP in which the dependence on the target parameter $\vtheta$ is added. As before, the MLP consists of 3 hidden layers with 128 units.
\begin{table}[h!]
    \centering
    \begin{tabular}{llllllll}
        \toprule
        & SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        \emph{Architecture} & MLP & MLP & MLP & MLP & MLP & CNN & MLP \\ 
        \emph{Batch-size} & 128 & 128 & 128 & 128 & 128 & 64 & 128 \\
        \emph{Coverage samples individual} & 100,000 & 100,000 & 100,000 & 100,000 & 100,000 & 10,000 & 100,000 \\
        \emph{Coverage samples ensemble} & 20,000 & 20,000 & 20,000 & 20,000 & 20,000 & 10,000 & 20,000 \\
        \emph{Epochs} & 100 & 100 & 100 & 100 & 100 & 100 & 100 \\
        \emph{Learning-rate} & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 \\
        \bottomrule
    \end{tabular}
    \caption{Architectures and hyperparameters associated with Neural Ratio Estimation.}
    \label{tab:npe_hyperparameters}
\end{table}

\subsection{Non-amortized}
All our implementations of non-amortized approaches rely on the reference implementation in \texttt{sbi} \citep{sbi}. We use the recommended defaults unless stated otherwise. Whenever available, the same MLP embedding network is used. It consists of 3 hidden layers with 64 units and SELU \citep{selu} activations. The latent space has a dimensionality of 10 features. For all sequential methods, we use 10 rounds to iteratively improve the posterior approximation.
\subsubsection{SNPE}
Our evaluations with \textsc{snpe} specifically use the \textsc{snpe-c} \citep{greenberg2019automatic} variant, as suggested by \texttt{sbi} \citep{sbi}.
To minimize inconsistencies between experiments, we use the defaults suggested by the \texttt{sbi} authors unless states otherwise. Specific changes are highlighted in Table \ref{tab:snpe_hyperparameters}.

\begin{table}[h!]
    \centering
    \begin{tabular}{llllllll}
        \toprule
        & SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        \emph{Batch-size} & 128 & 128 & 128 & 128 & 32 & Intractable & Intractable \\
        \emph{Coverage samples} & 300 & 300 & 300 & 300 & 300 & Intractable & Intractable \\
        \emph{Embedding} & MLP & MLP & MLP & MLP & MLP & Intractable & Intractable \\ 
        \emph{Epochs} & 100 & 100 & 100 & 100 & 100 & Intractable & Intractable \\
        \emph{Features} & 64 & 64 & 64 & 64 & 64 & Intractable & Intractable \\
        \emph{Model} & NSF & NSF & NSF & NSF & NSF & Intractable & Intractable \\
        \emph{Transforms} & 3 & 3 & 1 & 3 & 3 & Intractable & Intractable \\
        \emph{Rounds} & 10 & 10 & 10 & 10 & 10 & Intractable & Intractable \\
        \emph{Learning-rate} & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 & Intractable & Intractable \\
        \bottomrule
    \end{tabular}
    \caption{Architectures and hyperparameters associated with Sequential Neural Posterior Estimation.}
    \label{tab:snpe_hyperparameters}
\end{table}

\subsubsection{SNL}
In contrast to other sequential methods, our evaluations with \textsc{snl} \citep{papamakarios2019sequential} add two additional intractable benchmarks. At the root of this issue lies the dimensionality of the observable. In both cases, the dimensionality of observables caused memory issues in \textsc{snl}. In addition, training a seperate embedding model (that requires additional simulations) is outside of the scope of this work. For this reason, we consider the Lotka-Volterra en Spatial SIR benchmark to be intractable.

\begin{table}[h!]
    \centering
    \begin{tabular}{llllllll}
        \toprule
        & SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        \emph{Batch-size} & 128 & 128 & 128 & Intractable & Intractable & Intractable & Intractable \\
        \emph{Coverage samples} & 300 & 300 & 300 & Intractable & Intractable & Intractable & Intractable \\
        \emph{Epochs} & 100 & 100 & 100 & Intractable & Intractable & Intractable & Intractable \\
        \emph{Features} & 64 & 64 & 64 & Intractable & Intractable & Intractable & Intractable \\
        \emph{Model} & NSF & NSF & NSF & Intractable & Intractable & Intractable & Intractable \\
        \emph{Transforms} & 3 & 3 & 1 & Intractable & Intractable & Intractable & Intractable \\
        \emph{Rounds} & 10 & 10 & 10 & Intractable & Intractable & Intractable & Intractable \\
        \emph{Learning-rate} & 0.001 & 0.001 & 0.001 & Intractable & Intractable & Intractable & Intractable \\
        \bottomrule
    \end{tabular}
    \caption{Architectures and hyperparameters associated with Sequential Neural Likelihood.}
    \label{tab:snl_hyperparameters}
\end{table}

\newpage
\subsubsection{SNRE}
\begin{table}[h!]
    \centering
    \begin{tabular}{llllllll}
        \toprule
        & SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        \emph{Architecture} & MLP & MLP & MLP & MLP & MLP & Intractable & Intractable \\
        \emph{Batch-size} & 128 & 128 & 128 & 128 & 128 & Intractable & Intractable \\
        \emph{Coverage samples} & 300 & 300 & 300 & 300 & 300 & Intractable & Intractable \\
        \emph{Epochs} & 100 & 100 & 100 & 100 & 100 & Intractable & Intractable \\
        \emph{Features} & 64 & 64 & 64 & 64 & 64 & Intractable & Intractable \\
        \emph{Rounds} & 10 & 10 & 10 & 10 & 10 & Intractable & Intractable \\
        \emph{Learning-rate} & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 & Intractable & Intractable \\
        \bottomrule
    \end{tabular}
    \caption{Architectures and hyperparameters associated with Sequential Neural Ratio Estimation.}
    \label{tab:snre_hyperparameters}
\end{table}

\subsubsection{Approximate Bayesian Computation}
Our \textsc{abc} implementation relies on the \texttt{MCABC} and \texttt{SMCABC} classes in the \texttt{sbi} \citep{sbi} package.
The specific settings from Rejection \textsc{abc} and \textsc{smc-abc} are described in Tables \ref{tab:abc_hyperparameters} and \ref{tab:smcabc_hyperparameters} respectively.
The quantile specifically refers to the proportion of closest samples that were kept in the final posterior. Because our specific implementation our coverage requires the ability to describe the posterior density function, we relied on Kernel Density Estimation to estimate the posterior density from the accepted samples.
\begin{table}[h!]
    \centering
    \begin{tabular}{llllllll}
        \toprule
        & SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        \emph{Coverage samples} & 300 & 300 & 300 & 300 & 300 & Intractable & Intractable \\
        \emph{Quantile} & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & Intractable & Intractable \\
        \bottomrule
    \end{tabular}
    \caption{Hyperparameters associated with Rejection Approximate Bayesian Computation.}
    \label{tab:abc_hyperparameters}
\end{table}
\begin{table}[h!]
    \centering
    \begin{tabular}{llllllll}
        \toprule
        & SLCP & M/G/1 & Weinberg & Lotka-V. & Spatial SIR & GW & Streams \\
        \midrule
        \emph{Coverage samples} & 300 & 300 & 300 & 300 & 300 & Intractable & Intractable \\
        \emph{$\epsilon$ decay} & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & Intractable & Intractable \\
        \emph{Quantile} & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & Intractable & Intractable \\
        \bottomrule
    \end{tabular}
    \caption{Hyperparameters associated with Sequential Monte Carlo Approximate Bayesian Computation.}
    \label{tab:smcabc_hyperparameters}
\end{table}

%\section{Benchmarks}
%\label{appendix:benchmarks}
%\subsection{SLCP}
%\subsection{M/G/1}
%\subsection{Weinberg}
%\subsection{Lotka Volterra}
%\subsection{Spatial SIR}
%\subsection{Gravitational Waves}
%\subsection{Stellar Streams}

\clearpage
\newpage
\section{Additional results}
\label{sec:additional_results}
\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{figures/coverage_ensemble_size}
    \caption{Evolution of the empirical coverage probability with respect to ensemble size for various confidence levels. The results are obtained by training 100 ratio estimators (\textsc{nre}) on the \textsc{slcp} benchmark. A positive effect is observed in terms of empirical coverage probability and ensemble size, i.e., a larger ensemble size correlates with a larger empirical coverage probability. This is not unsurprising, because a larger ensemble is expected to capture more of the uncertainty that stems from the training procedure.}
    \label{fig:coverage_ensemble_size}
\end{figure}

\end{document}

### 2021-09-27 paper/main.tex
Update manuscript

@@
 \usepackage{acronym}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
 \usepackage{amsfonts}
@@
 \usepackage{color}
-\usepackage{fontawesome}
 \usepackage{graphics}
@@
 \usepackage{nicefrac}
-\usepackage{tikz}
 \usepackage{caption}
-\usepackage{subcaption}
-\usepackage{placeins}
-\usepackage{wrapfig}
 \usepackage{float}
-\usepackage{dsfont}
 \usepackage{tcolorbox}
@@
   bottom=2pt,
-  \centering #1
+  #1
 }
@@
 
-\begin{custombox}
+\protect\begin{custombox}
 {\bfseries Observation 1} All benchmarked algorithms produce non-conservative posterior approximations.
@@
 % Appendix
-\FloatBarrier
+\clearpage
 \newpage

### 2021-09-27 paper/main.tex
Add render

@@
 %
-\usepackage{aistats2022}
+\usepackage[accepted]{aistats2022}
 %
@@
 
-\newcommand{\gilles}[1]{\textcolor{orange}{GL: #1}}
-\newcommand{\antoine}[1]{\textcolor{green}{AW: #1}}
-\newcommand{\joeri}[1]{\textcolor{red}{JH: #1}}
-\newcommand{\arnaud}[1]{\textcolor{blue}{AD: #1}}
-\newcommand{\old}[1]{\textcolor{magenta}}
-
 % Custom definitions
@@
 %
-\runningtitle{Towards Drawing Scientific Conclusions with Simulation-Based Inference }
+\runningtitle{Towards Drawing Scientific Conclusions with Simulation-Based Inference}
 
@@
 \begin{abstract}
-
-%   In recent years a myriad of simulation-based inference algorithms have been developed
-%   with the objective to produce approximations as close as possible to the ground truth.
-%   In this work we take the position that minimizing a divergence between the approximation and an unknown ground truth can incorrectly drive scientific inquiry.
-Instead, we argue for conservativeness.
-Approximations should therefore always convey at least as much uncertainty as the ground truth, and never be overconfident.
-We assess conservativeness by measuring coverage and showcase through extensive experiments that various approaches in simulation-based inference can produce non-conservative posterior estimators.
-We show empirically that ensembles consistently help in this regard but can still lead to non-conservative posterior estimators.
-Finally, we discuss several perspectives and open avenues of research towards conservative estimators.
-
-% My pass:
-%
-%
-%Computer simulators are at the center of many scientific disciplines.
-%Although modern simulators are able to describe complex processes, they are less suited
-%for statistical inference. 
-%At the core of this problem lies the intractable likelihood model implicitly defined by the simulator's computer code. 
-%To deal with this intractability,
-%a myriad of Bayesian inference algorithms have been developed to approximate
-%posteriors as possible to their unknown ground truths. The only requirement of these algorithms being that generating simulations is possible.
-%In this work, we take the position that minimizing a divergence between the approximation and an unknown ground truth can incorrectly drive scientific inquiry. Instead, we
-%argue for conservative approximations, meaning that they should always convey at least as much uncertainty as the ground truth. We collect extensive
-%empirical evidence spanning months of computation on several computer clusters. Our results indicate that all benchmarked techniques produce non-conservative posterior
-%approximations. Complicating their applicability.
-%We show that ensembles are consistently more reliable in this regard, but can still lead to non-conservative
-%estimators. Our study is complemented with new research proposals to strengthen the
-%application of simulation-based inference in the sciences.
-
-%\joeri{Reworked Gilles' proposal a bit. See below.}
-
-% 
-% Joeri's proposal after Gilles' proposal
-%
-%
-
-%Recent years have seen tremendous innovations in the field of Bayesian simulation-based inference.
-%{\color{blue} This work takes a step back by assessing the reliability of these algorithms to scientific use-cases concerned with constraining parameters, as is often the case in the physical sciences.???
-We present...}
-%This work presents extensive empirical evidence that all benchmarked algorithms -- including \textsc{(s)nre}, \textsc{(s)npe}, \textsc{snl} and various forms of \textsc{abc} -- produce non-conservative posterior approximations.
-Making these algorithms demonstrably unreliable if one's scientific goal is to constrain parameters of interest, as is often the case in the physical sciences.
-Our results further demonstrate that ensembles are consistently more reliable in this regard, although they may still lead to non-conservative posterior approximations.
-%We argue that failing to address this issue will lead to a well-founded distrust in simulation-based inference.
-For this reason we argue that research efforts should now focus on theoretical and methodological advances to guarantee conservative approximate inference.
-
-%
-% Gilles proposal
-%
 We present extensive empirical evidence showing that current Bayesian simulation-based inference algorithms are inadequate for the falsificationist methodology of scientific inquiry.
@@
 
-% \\\joeri{Which version? Merge?}
-
-% In recent years a myriad of simulation-based inference algorithms have been developed to perform Bayesian inference with an intractable likelihood implicitly defined by a simulator.
-Those algorithms traditionally have as objective to produce approximate posterior over the quantity to be inferred as close as possible to the ground truth posterior.
-In this work, we take the position that minimizing a divergence between the approximation and an unknown ground truth can lead to overconfident approximations and hence incorrectly drive scientific inquiry.
-Instead, we argue for conservativeness meaning that approximations should therefore always convey at least as much uncertainty as the ground truth, and never be overconfident.
-Our main contribution lies in the generation through month of computation of extensive empirical evidence that all currently existing approaches in simulation-based inference can produce non-conservative posterior estimators and are hence not suited for scientific purpose as they are.
-We show empirically that ensembles consistently help in this regard but can still lead to non-conservative posterior estimators and discuss several perspectives and open avenues of research towards conservative estimators.
-
 \end{abstract}
@@
 \section{Introduction}
-
-% Many scientific disciplines rely on computer simulations to study complex phenomena under various conditions. 
-% Although modern simulators can generate realistic synthetic observables through detailed descriptions of their data generating processes, 
-% they are unfortunately not suitable for statistical inference.
-% At the core of this issue lies the likelihood model $p(\vx\vert\vtheta)$ implicitly defined by 
-% computer code describing the data generating processes.
-% The direct evaluation of the likelihood rests on the \emph{intractable} integration of all stochastic execution paths, rendering statistical inference based on the likelihood impractical.
-% Fortunately, inference remains possible by relying on likelihood-free \emph{approximations} \citep{cranmer2020frontier}
-% within a field referred to as simulation-based or likelihood-free inference.
 
@@
 All code related to this manuscript is available at
-\href{https://github.com/anonymous/anonymous}{\texttt{github.com/anonymous/anonymous}}.
-%\href{https://github.com/JoeriHermans/troubles-in-paradise}{\texttt{github.com/montefiore-ai/troubles-in-paradise}}
-
-%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, the natural sciences make decisions based on frequentist confidence intervals or Bayesian credible regions.
-
-%Although simulation-based inference targets domain sciences, advances in the field are mainly driven from a machine learning perspective.
-%The field therefore inherits the quality assessments \citep{lueckmann2021benchmarking} customary to the machine learning literature which usually involves maximizing some criterion.
-Despite recent developments of post hoc diagnostics to inspect the quality of likelihood-free approximations \citep{cranmer2015approximating, Brehmer:2018eca, brehmer2019mining, Hermans:2020skz, lueckmann2021benchmarking, sbc, dalmasso2020confidence}, the problem concerning \emph{scientific conclusions} based on simulation-based inference remains: \emph{can these techniques be used to drive scientific research whenever their fitting criteria are not globally optimized or the availability of data is limited?}
-
-%{\bfseries sciences are rather concerned with
-%\emph{excluding} hypotheses at some confidence level}
-
-%As an illustration of this, a recent application consist in inferring the nature (cold or warm) and mass of dark matter through the observation of the evolution of stellar streams' density.
-The simulator evolves a stream and its stellar density through a stochastic iterative process though interactions with a family of dark matter subhaloes parametrized though the mass of the dark matter \arnaud{where does the nature appear?}.
-The iterative nature of the simulator leads to an intractable likelihood since evaluating it would require to consider all execution paths.
-\joeri{Rewrite}
-
-%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, the natural {\bfseries sciences are rather concerned with
-%\emph{excluding} hypotheses at some confidence level}
-%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, a common concern in natural {\bfseries sciences is rather to \emph{exclude} hypotheses at some confidence level}.
-
-%For this reason, domain scientists want guarantees to whether statistical \emph{approximations} have confidence intervals (frequentist) or credible regions (Bayesian) not smaller than they should be.
-In this work we adopt the Bayesian point of view, and are then concerned with not rejecting viable parameters from the credible region and incorrectly drive scientific inquiry.
-%If that would \emph{not} be the case, scientists could reject viable hypotheses and incorrectly drive scientific inquiry.
-
-%Considering the example of the inference of the nature and mass of dark matter based on the observation of a stellar streams, incorrectly inferring the nature can have a disastrous cascading effects.
-Those can be found in the field of particle physics where excluding warm dark matter would exclude the hypothesized sterile neutrino.
-\arnaud{refs} On the contrary, if cold dark matter were to be excluded, the theory for the disruptions of stellar streams would not hold.
-
-%{\bfseries what guarantees or properties do these techniques have whenever their fitting criteria are not globally optimized or the availability of data is limited?}
-
-% Every result and figure is annotated with \code{https://github.com/montefiore-ai/troubles-in-paradise}, linking to the code used to generate it.
-
-%Despite recent methodological developments~\gilles{refs} and successes across various scientific use cases~\gilles{refs}, a major criticism of simulation-based inference is that the involved statistical computations are essentially not verifiable and are therefore not suitable for scientific disciplines whose primary objective is to \emph{constrain} parameters of interest, or \emph{exclude} models at a certain confidence level.
-
-%We emphasize that algorithms should not just show high performances \arnaud{rephrase}.
-In the case of Bayesian posterior inference, domain scientists should also have guarantees that credible regions identified with approximate posteriors are not smaller than they should be, since rejecting parameter values compatible with the data will drive the scientific inquiry to wrong conclusions.
-\arnaud{this is the case with ...
-concrete example, gw, streams and refs}
-
-%These concerns have led to further work focusing on improving the accuracy of inference procedures~\gilles{refs} and to the development of post hoc diagnostics to inspect the quality of their approximations~\citep{cranmer2015approximating, Brehmer:2018eca, brehmer2019mining, Hermans:2020skz, lueckmann2021benchmarking}.
-%Despite these innovations, it remains unanswered what formal guarantees these techniques have whenever their approximations are not optimal, or equivalently, whenever their fitting criteria are not globally optimized.
-
-%Theoretical characterizations of simulation-based techniques are critically needed to draw scientific conclusions reliably. 
-%In this work, we study the empirical coverage of various simulation-based inference techniques over multiple benchmarks and first demonstrate that all those techniques may lead to credible regions that are too narrow with respect to the ground truth, hence leading to Type-I errors and possibly to wrong scientific conclusions.
-%We argue that model regularization constitutes a potential solution and provide a critical discussion about the ability to diagnose such pathologies.
-The paper is outlined as follows.
-\arnaud{Update paper structure} Section~\ref{sec:background} outlines the statistical formalism and the necessary background of simulation-based inference.
-We briefly highlight the importance of a proper diagnostic to inspect the statistical quality of the approximations.
-Section~\ref{sec:method} outlines our theoretical results and proposed methodology, supported by experimental validation in Section~\ref{sec:experiments}.
+\href{https://github.com/montefiore-ai/crisis-in-sbi}{\texttt{github.com/montefiore-ai/crisis-in-sbi}}
 \section{Background}
@@
 
-%which can either be the posterior itself. Or the likelihood-to-evidence ratio 
-%$$r(x\vert\vartheta) = \frac{p(x \vert \vartheta)}{p(x)}.$$ 
-%Through approximations $\hat{r}(x\vert\vartheta)$, evaluating estimates of the posterior density function amount to computing the product of the \emph{tractable} prior probability $p(\vartheta)$ and the estimated likelihood-to-evidence ratio $\hat{r}(x\vert\vartheta)$.
-An unormalized approximate of the posterior can also be recovered from a surrogate for the likelihood by multiplying it to the prior probability.
-
-%\subsection{Likelihood-free inference methods}
 \subsection{Statistical quality assessment}
-%The work of \citet{lueckmann2021benchmarking} benchmarks common simulation-based
-%techniques on various metrics. Although the benchmarks are done very thoroughly with respect to the \emph{selected} metrics, 
-%there are issues regarding their \emph{applicability}.
-
 \begin{figure}[b!]
@@
 Even if such evaluations would hypothetically be possible,
-there are no criteria to what constitutes an \emph{acceptable} estimator.
-%for scientific use-cases.
+there are no criteria to what constitutes an \emph{acceptable}
 In addition, it is not possible to know for certain whether the classifier or kernel used to measure the diverge are sufficiently expressive to detect differences between the approximation and said posterior.
@@
 of $\hat{p}(\vtheta\vert\vx)$.
-%\begin{equation}
-%\mathbb{E}_{(\vtheta^*, \vx_o) \sim p(\vtheta, \vx)} \left\{ \begin{array}{ll}
-%    1 & \text{if } \vtheta^* \in \Theta_{\hat{p}(\vtheta|\vx = \vx_o)}(1 - \alpha) \\
-%    0 & \text{otherwise}
-%\end{array} \right..
-%\end{equation}
 \end{definition}
@@
 \end{definition}
-% \begin{definition}
-% The {empirical \bfseries coverage probability} of a posterior estimator at a confidence level $1 - \alpha$ given a set of $n$ i.i.d. samples $(\vtheta^*,\vx)\sim p(\vtheta,\vx)$
-% is
-% \begin{equation}
-% \frac{1}{n} \sum_{i=1}^n \left\{ \begin{array}{ll}
-%     1 & \text{if } \vtheta^*_i \in \Theta_i \\
-%     0 & \text{otherwise}
-% \end{array} \right.,
-% \end{equation}
-% where $\Theta_i$ is the credible region computed through the posterior approximation $\hat{p}(\vtheta\vert\vx=\vx_i)$ considering that $\vx_i \sim p(\vx\vert\vtheta = \vtheta^*_i)$.
-% \end{definition}
-% \begin{definition}
-% The {\bfseries nominal coverage probability} is effectively equal to the confidence level.
-% \end{definition}
-% \begin{definition}
-% An estimator is deemed acceptable if it {\bfseries has coverage} at the confidence level of interest.
-That is, whenever the empirical coverage probability is {\bfseries larger or equal} to the nominal coverage probability.
-% \end{definition}
-% \begin{definition}
-% A {\bfseries conservative estimator} is an estimator that has coverage for {\bfseries all} confidence levels.
-% \end{definition}
 Although coverage is a necessary metric to assess conservativeness, it is limited in its ability to determine the information gain a posterior (approximation) has over its prior.
@@
 \subsubsection{Amortized}
-%from  posterior $p(\vartheta|x_0)$ for an observable $x_0$.
-Candidates parameters $\vartheta_i$ are first sampled from the prior, $p(\vartheta)$.
-Those parameters are then used along with the simulator to produce observations $x_i$.
-The candidate parameters that have produced the closest observations to the target observation $x_0$ according to some distance metric are kept and considered samples from the posterior, $p(\vartheta|x_0)$.
-\arnaud{add details?: norm 2 distance + quantile 0.01 with at least 100 samples?}
-%Sequential Monte-Carlo ABC (SMC-ABC) \citep{10.1093/bioinformatics/btp619, sisson2007sequential, beaumont2009adaptive} iteratively update a set of particules to match the posterior distribution.
-At each iteration, candidate parameters that produced the highest distance are discarded and new candidates are generated by adding a perturbation to the remaining candidates.
-\arnaud{double check that this is correct}
 {\bf Neural Posterior Estimation} (\npe) is concerned with directly learning an amortized estimator $\hat{p}_\psi(\vtheta\vert \vx)$ to the posterior with normalizing flows.
@@
 \textsc{abc} approximations are \emph{only exact} whenever the summary statistic is sufficient \emph{and} the acceptance threshold $\epsilon$ tends to 0 \citep{sisson2018overview}.
-% Note that
-% amortized estimates of the likelihood-to-evidence ratio $r(x\vert\vartheta)$ can be computed through $\hat{p}_\psi(\vartheta\vert x)$ because
-% $\log r(x\vert\vartheta) \approx \log \hat{p}_\psi(\vartheta\vert x) - \log p(\vartheta)$.
-Therefore, the binary discriminator $\hat{d}(\vartheta,x)\triangleq\sigmoid(\log\hat{p}_\psi(\vartheta\vert x) - \log p(\vartheta))$ enables $\hat{p}_\psi(\vartheta,x)$ to be {\bf learned by minimizing
-% the binary cross entropy criterion} presented above. All flow-based estimators in this work are optimized using the aforementioned criterion unless stated otherwise.
-% \joeri{We can remove this right? Yes my bad}
-% Once trained, we can sample new data points from the modeled distribution as well as evaluate the density of new data points.
-We highlight two possibilities for building an approximate amortized posterior $p_\psi(\vartheta|x)$ with NFs.
-First, by direct minimization of the \textsc{kl} divergence between the approximate posterior and the actual posterior,
-% \begin{align}
-%     \psi^* &= \argmin_\psi \mathbb{E}_{p(x)}\left[\textsc{kl}(p(\vartheta|x)~\vert\vert ~p_\psi(\vartheta|x)\right] = \argmin_\psi \mathbb{E}_{p(x)}\mathbb{E}_{p(\vartheta|x)}\left[\log\frac{ p(\vartheta|x)}{p_\psi(\vartheta|x)}\right]\\
-%     &= \argmax_\psi \mathbb{E}_{p(\vartheta,x)}\left[\log p_\psi(\vartheta|x)\right].
-% \end{align}
-% \antoine{Say it is equivalent to MLE. (amortized over posteriors)}
-% The second option is to define the NF likelihood-to-evidence ratio as 
-% \begin{align}
-%     r_\psi(x|\vartheta) := \frac{p_\psi(\vartheta|x)}{p(\vartheta)},
-% \end{align}
-% and to train it as a classifier-based amortized ratio estimator.
-% \antoine{Add the two training methods have the same optimum but the second may be tuned to be blablabla as shown later}
-% \joeri{My take below?}
-
-%{\bfseries Sequential methods} aim at estimating the posterior for a specific observable $x_o$ by dedicating the simulation budget to iteratively improve an approximation.
-%These methods alternate between a training and a simulation phase, the latter being designed to take \emph{current} knowledge into account such that subsequent simulation parameters $\vartheta$ are expected to produce observables $x$ closer to $x_o$ compared to previous iterations.
 
@@
 \subsection{Results}
+\protect\begin{custombox}
+{\bfseries Observation 1} All benchmarked algorithms produce non-conservative posterior approximations.
+This pathology tends to be accentuated when using a small simulation-budget in both amortized and non-amortized approaches.
+
+\medskip
+
+{\bfseries Observation 2} For a given simulation budget, amortized approaches have the tendency to be more conservative than non-amortized approaches.
+
+\medskip
+
+{\bfseries Observation 3} The empirical coverage probability of an ensemble model is larger than the expected individual model.
+The ensemble size positively affects the empirical coverage probability as well.
+
+\medskip
+
+{\bfseries Observation 4} Amortized methods are not subordinate with respect to the simulation-efficiency of non-amortized sequential methods, especially when taking hyper-parameter tuning and the evaluation of the coverage diagnostic into account.
+\end{custombox}
 \begin{figure*}[h!]
@@
 \begin{figure*}[h!]
-    %\includegraphics[width=\textwidth]{figures/coverage_multi_ensemble.pdf}
     \includegraphics[width=\textwidth]{figures/coverage_multi_ensemble_with_bagging.pdf}
@@
 
-% In Figure \ref{fig:coverage_ensemble} we observe that the empirical coverage probability of the ensemble models is consistently larger than the empirical coverage probability of the expected individual estimator.
-Individual estimators only captures aleatoric uncertainty, i.e., uncertainty that is linked to stochasticity of the data generation procedure.
-Ensembles are expected to also capture part of the epistemic uncertainty, i.e., uncertainty issued by the lack of knowledge.
-In particular, ensembles capture the uncertainty related to the training procedure.
-This added uncertainty results in a larger credible region increasing the empirical coverage probability.
-Although ensembles take part of the epistemic uncertainty into account, they can still produce non-conservative posteriors.
-% Current applications of simulation-based inference can therefore rely on ensembling to build increasingly conservative posterior estimators.
-% It should be noted however that bagging does not yield a similar effect.
-% As shown in Appendix \ref{sec:additional_results}, a positive effect with respect to ensemble size is observed.
 In Figure \ref{fig:coverage_ensemble} we observe that the empirical coverage probability of ensemble models is consistently larger than the empirical coverage probability of the expected individual posterior estimator.
@@
 
-\medskip
-
-\protect\begin{custombox}
-{\bfseries Observation 1} All benchmarked algorithms produce non-conservative posterior approximations.
-This pathology tends to be accentuated when using a small simulation-budget in both amortized and non-amortized approaches.
-
-\medskip
-
-{\bfseries Observation 2} For a given simulation budget, amortized approaches have the tendency to be more conservative than non-amortized approaches.
-
-\medskip
-
-{\bfseries Observation 3} The empirical coverage probability of an ensemble model is larger than the expected individual model.
-The ensemble size positively affects the empirical coverage probability as well.
-
-\medskip
-
-{\bfseries Observation 4} Amortized methods are not subordinate with respect to the simulation-efficiency of non-amortized sequential methods, especially when taking hyper-parameter tuning and the evaluation of the coverage diagnostic into account.
-\end{custombox}
 \section{Discussion}
@@
 A theoretical understanding of these frameworks in the context of simulation-based inference would further strengthen their applicability.
-% Our results show that ensembling constitutes a promising research direction.
-A theoretical understanding for the observation that ensembles produce increasingly conservative posteriors would further strengthen their applicability.
-In addition, the idea of capturing epistemic uncertainty with ensembles could further be extended using the \emph{Bayesian Deep Learning} framework, which attempts to model an approximate posterior over the weights of a neural network given the available data.
-The Bayesian framework assigns a clear interpretation to those uncertainties because they arise from the prior and likelihood.
-On the other hand, the uncertainty in ensembles arise from the stochasticity during training.
-% In addition, the idea of capturing epistemic uncertainty with ensembles could further be extended using the \emph{Bayesian Deep Learning} framework, which attempts to model an approximate posterior over the weights of a neural network given the available data.
-In the likelihood-free setting, this data would be issued from the simulator.
-The posterior for a given observable would subsequently be obtained by marginalizing the posterior over the available weights.
-As with ensembles, the posterior over the weights takes epistemic uncertainty into account, which is the uncertainty issued by the lack of knowledge.
-The Bayesian framework assigns a clear interpretation to those uncertainties because they arise from the prior and likelihood.
-The uncertainty in ensembles on the other hand arise from the stochasticity in the training procedure.
 
